---
title: "LastName Homework 1"
author: "Kat Leigh"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1:
## Detective work to decipher an unintelligible function

### Rewrite the R code so that its purpose can be easily understood. Include:
  •comments,
  •meaningful variable names,
  •indenting, line spacing, etc.

```{r}
# function to add an inset tag to a plot.
## 'xtrm_coords' defines the max/min x and y values of the plot.
## 'inst_lab' is the text label you want to appear for the inset.
## 'injst' is a vector of the adjustment for the label inside the plot. The first item shifts the label to the right from the y axis, while the second item shifts the label up from the x axis.
## the function scales the adjustment specified in injst to the plot, creating the two variables 'x_loc' and 'y_loc' which specify the x and y coordinates, respectively, for the inset to appear.

inst_fxn <- function(inst_lab, injst, ...){
  xtrm_coords <- par("usr")
  x_loc <- xtrm_coords[1] + injst[1]*diff(xtrm_coords[1:2])
  y_loc <- xtrm_coords[3] + injst[2]*diff(xtrm_coords[3:4])
  text(x=x_loc, y=y_loc, l=inst_lab, ...)
}

# make a plot
plot(1,1)
# run the function to insert the inset label
inst_fxn(inst_lab= "(a)", injst= c(.05,.95))
```
# Question 2: Central Limit Theorem
## 2a. Write the function!
### Write a function named CL.theorem() that takes four parameters (i.e., arguments): n, mean, sd, breaks.
### The function will draw n numbers from a random normal distribution with a mean of mean, and a standard deviation of sd. The function will then plot a histogram of the resulting values with the breaks specified by the breaks parameter. The function will also return a list of the following named elements:
•a vector of the randomly drawn numbers; name this element data
•n; name this element n_data
•the mean of the n randomly drawn numbers; name this element mean
•the standard deviation of the n randomly drawn numbers; name this element sd

### Use the following code to test your function:

```{r}
CL.theorem <- function(n, mean=5, sd=2, breaks=seq(from=-5,to=15,by=0.5)){
  distrib <- rnorm(n, mean, sd)
  histz <- hist(distrib, breaks=breaks,
                xlab='Bins', ylab='frequency', main= 'Distribution of data')
  
  return(list(histz, data= distrib, n_data= n, mean= mean(distrib), sd= sd(distrib)))
}

q1 <- CL.theorem(n=5, mean=5, sd=2, breaks=seq(from=-5,to=15,by=0.5))
q1$data
q1$n_data
q1$mean
q1$sd

```
## 2b. Make multiple plots!
### Use the pdf() function for this question. Now, open a pdf file for output to store the plots, and call the function 10 times with the same values for mean, sd, breaks, but with different values for n, as follows: n=5, 10, 20, 30, 50, 100, 500, 1000, 5000, 10000. Then close the pdf file. The result should be a single pdf file containing 10 plots.

```{r}
n_lst <- c(5, 10, 20, 30, 50, 100, 500, 1000, 5000, 10000)

pdf(file='ten_plots')

try_for_loop <- for(i in 1:length(n_lst)){
  CL.theorem(n_lst[i], mean=5, sd=2, breaks=seq(from=-5,to=15,by=0.5))
}

dev.off()
```

## 2c. Remember the apply() family?
### Solve question 2b using the apply() function (i.e., open a pdf file, use the apply() function, close the pdf file).

```{r}
pdf(file='ten_plots_sapply')

try_apply <- sapply(X=n_lst, FUN=CL.theorem)

dev.off()

```

